### 2011-01-26 paper/platformDetails.tex
added period.

\editbox{write this, old quadratot System Architecture and Implementation section below.}

@@

The robot is run using a given motion model, including, if desired, 
smooth interpolation over time for the beginning and end of the run. 
The servos are prevented from being commanded to a point outside their
normal range (0 - 1023) as well as beyond points where limbs would collide

>>>>

@@

The robot is run using a given motion model, including, if desired, 
smooth interpolation over time for the beginning and end of the run. 
The servos are prevented from being commanded to a point outside their
normal range (0 - 1023) as well as beyond points where limbs would collide.
